OpenMPIR

### 2017-09-08 paper.tex
More references
Removed addressed note

Addressing these concerns this is a major motivation for our use of Tapir.
\pmnote{This made me remember that Rice and Cray folks did some work on extending LLVM
to reason about PGAS-like constructs We should probably call that out in 
this discussion -- that said, I don't recall their approach being general so it 
does not quite fit the discussion here but I'd have to think a bit harder if it
would be possible to capture something like MPI operations in some fashion... 
I will email George a pointer to the paper...} 
By standardising an IR, in addition to easing the development of optimizations,
one avoids duplicating work across different implementations. It also enables
the possibility of multiple programming models coexisting peacefully. We'll
return to this issue later in Section~\ref{Sec:Discussion} when discussing
future work.

@@

First, compilers can attach metadata to an existing IR. For example, LLVM has a
parallel loop metadata construct \cite{}. This has the benefit of being
flexible and requiring minimal work, but historically can be lost during
optimizations, and any code movement can break the semantics. The flexibility
of this approach can also be viewed as a negative, as it can compromise
what can otherwise be a simple, well defined semantics for the IR.

>>>>

Addressing these concerns this is a major motivation for our use of Tapir.  By
standardising an IR, in addition to easing the development of optimizations,
one avoids duplicating work across different implementations. It also enables
the possibility of multiple programming models coexisting peacefully. We'll
return to this issue later in Section~\ref{Sec:Discussion} when discussing
future work.

@@

First, compilers can attach metadata to an existing IR. For example, LLVM has a
parallel loop metadata construct \cite{llvmref}. This has the benefit of being
flexible and requiring minimal work, but historically can be lost during
optimizations, and any code movement can break the semantics. The flexibility
of this approach can also be viewed as a negative, as it can compromise
what can otherwise be a simple, well defined semantics for the IR.
